Navigating Through Crisis: The Influence of COVID-19 on Canada’s Mental Health Problem

### 2024-04-22 paper/paper.qmd
Updated paper

For both sexes combined, the overall trend is less erratic, pointing to the importance of disaggregating data by gender to fully capture the differential impacts on mental health. These findings highlight the significance of gender-responsive mental health resources and interventions, particularly in addressing the unique challenges that have emerged during the pandemic.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trend4
#| fig-cap: Perceived mental health fair or poor in Canada

@@

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trend4
#| fig-cap: Perceived mental health fair or poor in Canada

@@

@@

Métis women, Indigenous women, and First Nations women report similar rates of around 30-31%, indicating the pressing mental health concerns among Indigenous populations. Historical context, ongoing systemic inequalities, and intergenerational trauma are likely contributing factors and underscore the importance of providing culturally competent care and support.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-trend2
#| fig-cap: Perceived mental health fair or poor in Canada

>>>>

For both sexes combined, the overall trend is less erratic, pointing to the importance of disaggregating data by gender to fully capture the differential impacts on mental health. These findings highlight the significance of gender-responsive mental health resources and interventions, particularly in addressing the unique challenges that have emerged during the pandemic.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-gender1
#| fig-cap: Perceived mental health fair or poor in Canada

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-gender2
#| fig-cap: Perceived mental health fair or poor in Canada

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-age1
#| fig-cap: Perceived mental health fair or poor in Canada

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-age2
#| fig-cap: Perceived mental health fair or poor in Canada

@@

Métis women, Indigenous women, and First Nations women report similar rates of around 30-31%, indicating the pressing mental health concerns among Indigenous populations. Historical context, ongoing systemic inequalities, and intergenerational trauma are likely contributing factors and underscore the importance of providing culturally competent care and support.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: fig-other
#| fig-cap: Perceived mental health fair or poor in Canada
